We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-01 paper/paper.tex
+ 1 paragraph

Figure \ref{fig:scatter_width} summarizes the results for the plane
width distributions.
The panel on the left compares the results for the MW and M31
observations against its randomized version. 
The most interesting outcome is that the MW plane width is smaller
than $95\%$ of the planes computed from the randomized distribution,
while the M31 plane width is consistent with the same distribution.

@@

The right panel shows the normalized results. 
This highlights the two results mentioned above.
First, the MW shows a low $c/a$ ration $2.5$ standard deviations away
from the mean value of the spherical distribution; this contrasts the
results for M31 which are close to $1$ standard deviation away.
Second, the less massive halos in the Illustris simulation present a
smaller dispersion in their deviations from sphericity than the
its masssive partner.

These

>>>>

Figure \ref{fig:scatter_width} summarizes the results for the plane
width distributions.
The panel on the left compares the results for the MW and M31
observations against its randomized version. 
The most interesting outcome is that the MW plane width is smaller
than $\approx 98\%$ of the planes computed from the randomized distribution,
while the M31 plane width is consistent with the same distribution.

@@

The right panel shows the normalized results. 
This highlights the two results mentioned above.
First, the MW shows a low $c/a$ ration close to two standard deviations away
from the mean value of the spherical distribution; this contrasts the
results for M31 which are close to $1$ standard deviation away.
Second, the less massive halos in the Illustris simulation present a
smaller dispersion in their deviations from sphericity than the
its masssive partner.
The MW axis ratio smaller than $\approx 98\%$ of the randomized
satellite distributions.   and its atipicallity is only comparable to
one halo in the Illustris  simulation (none in the ELVIS simulation).
